### 2017-04-26 src/problem.tex
moved to lualatex
going to sleep

We are given a virtual DAG $D_v = (V_v, A_v)$ 
with a source and destination vertices $s_v, t_v$ respectively, 
a physical DAG $D_p = (V_p, A_p)$
with a source and destination vertices $s_p, t_p$ respectively,
demand functions $p_d : V_v \to \R$, $b_d : E_v \to \R$,
capacity functions $p_c : V_p \to \R$, $b_c : E_p \to \R$,
and a cost function $c: V_v \times V_p \to \R$.

@@

\begin{figure}[ht]
\centering
\scalebox{.87}{
\input{fig-embedding}
}

>>>>

We are given a virtual DAG $D_v = (V_v, A_v)$ 
with source and destination vertices $s_v, t_v$ respectively, 
a physical DAG $D_p = (V_p, A_p)$
with source and destination vertices $s_p, t_p$ respectively,
demand functions $p_d : V_v \to \R$, $b_d : E_v \to \R$,
capacity functions $p_c : V_p \to \R$, $b_c : E_p \to \R$,
and a cost function $c: V_v \times V_p \to \R$.

@@

\begin{figure}[ht]
\centering
\scalebox{1}{
\input{fig-embedding}
}
